Revisiting the hydrodynamic wave modulation from linear wave theory

### 2024-08-26 paper/paper.tex
Switch to JFM template

\documentclass[draft]{agujournal2019}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
\usepackage{soul}
\linenumbers

\draftfalse

\journalname{JGR: Oceans}

\begin{document}

%\title{Dispersion of short waves riding on longer waves}
\title{Revisiting the hydrodynamic wave modulation from linear wave theory}

\authors{Milan Curcic\affil{1,2}}

\affiliation{1}{
  Rosenstiel School of Marine, Atmospheric, and Earth Science,
  University of Miami,
  Miami, FL
}
\affiliation{2}{
  Frost Institute for Data Science and Computing,
  University of Miami,
  Coral Gables, FL
}

\correspondingauthor{Milan Curcic}{mcurcic@miami.edu}

\begin{keypoints}
\item We revisit analytical and numerical solutions for hydrodynamic modulation of short waves by longer waves.
\item We present a higher-order analytical solution based on linear wave theory.
\item In contrast to an earlier study, we find stable numerical solutions for modulation by long-wave groups.
\end{keypoints}

\begin{abstract}
Hydrodynamic modulation of short ocean surface waves by longer ambient waves is
a well-known ocean surface process that affects remote sensing, the
interpretation of \textit{in situ} wave measurements, and numerical wave
forecasting.
In this paper, we revisit the linear wave theory and derive higher-order
solutions for the change of short-wave wavenumber, action density, and
gravitational acceleration due to the presence of longer waves.
We validate the analytical solutions with numerical simulations of the full wave
crest and action conservation equations.
The nonlinear analytical solutions of short-wave wavenumber, amplitude, and
steepness modulation significantly deviate from the linear analytical solutions
of \citeA{longuet1960changes}, and are similar to the nonlinear numerical
solutions by \citeA{zhang1990evolution}.
We also discuss the result of \citeA{peureux2021unsteady} who found through
numerical simulations that the short-wave modulation grows unsteadily with
each long-wave phase.
Here we show that this unsteady growth only occurs for homogeneous initial
conditions and does not occur for more realistic long-wave groups.
Finally, the combined analytical and numerical framework allows us to quantify
the contribution of various terms in the full wave conservation equations.
The new analytical solutions are a good approximation of the full numerical
solution in long-wave steepness up to $\approx 0.2$.
\end{abstract}

\section*{Plain Language Summary}
The ocean surface is typically covered by waves of many wavelengths.
Longer waves bunch up and dilate the shorter waves, and this process is
important to consider for both the measurements and the forecasting of ocean
waves.
Although there have been analytical and numerical solutions for how the short
waves should change in the presence of longer waves, they have either been
simplistic or 
This paper revisits and extends these solutions to propose a more accurate
description of how the short waves should change in the presence of longer
waves.

@@

Short ocean surface waves are modulated by longer swell.
Following the result by \citeA{unna1941white,unna1942waves,unna1947sea},
\citeA{longuet1960changes} introduced an analytical solution for hydrodynamic
modulation of short waves at the crest of an underlying longer wave:

\begin{equation}
\label{eq:lhs1960wavenumber}
\widetilde{k} = k (1 + \varepsilon_L)
\end{equation}
where $\widetilde{k}$ and $k$ are modulated and unmodulated short-wave wavenumbers,
respectively, and $\varepsilon_L = a_L k_L$ is the steepness of the long wave with
wavenumber $k_L$ and amplitude $a_L$.
This result has been influential on the development of remote sensing of ocean
surface waves and currents \cite{keller1975microwave,hara1994hydrodynamic}.
\citeA{longuet1987propagation} revisited this problem by considering variation
in the gravitational acceleration and fully non-linear wave numerical solutions
to find significantly stronger modulation than that predicted by
Eq. \ref{eq:lhs1960wavenumber}.
\citeA{zhang1990evolution} evaluated the effects of nonlinearity of short waves
using a non-linear Schr\" odinger equation and found higher wavenumber
modulation but lesser amplitude modulation than those predicted by
\citeA{longuet1987propagation}.
More recently, \cite{peureux2021unsteady} simulated the full wave conservation
equations and found that the short waves grow unsteadily due to the propagation of
longer waves, suggesting that the steady-state solutions may only be valid for
a few long-wave periods before the short waves are steep enough to break.

\begin{table}[h]
\label{table:modulation_literature_summary}
\caption{
  Summary of prior
  \cite{longuet1960changes,phillips1981dispersion,longuet1987propagation,zhang1990evolution,peureux2021unsteady}
  and present (this paper) approaches to calculating the modulation of short
  waves by long waves.
  *: long 3rd order Stokes wave is considered only in numerical simulations.
}
\begin{tabular}{cccccc}
\hline
Reference   & Governing & Gravity & Nonlinear  & Nonlinear   & Solution \\
            & equations & varies  & long waves & short waves &          \\
\hline
\hline
L-HS 1960   & Velocity potential       & No  & No  & No  & Analytical \\
\hline
P 1981      & Crest and energy         & Yes & Yes & No  & Numerical \\
            & conservation             &     &     &     &           \\
\hline
L-H 1987    & Velocity potential       & Yes & Yes & No  & Numerical \\
\hline
ZM 1990     & Nonlinear Schr\" odinger & Yes & Yes & Yes & Numerical \\
            & equation                 &     &     &     &           \\
\hline
PAG 2021    & Crest and action         & Yes & No & No  & Numerical \\
            & conservation             &     &     &     &           \\
\hline
This paper  & Crest and action         & Yes & Yes* & No  & Analytical \\
            & conservation             &     &      &     & and numerical \\
\hline
\end{tabular}
\end{table}

@@

\begin{equation}
\label{eq:dispersion}
\omega = \sqrt{gk} + k U
\end{equation}
where $\omega$ is the angular frequency, $g$ is the gravitational acceleration,
$k$ is the wavenumber, and $U$ is the mean advective current in the direction
of the wave propagation.
A current in the direction of the waves thus increases its absolution frequency,
wavenumber remaining unchanged.
An important limitation here is that $U$ must be slow-varying on the scales of
the wave period \cite{bretherton1968wavetrains}.
In the context of short waves riding on long waves, the mean advective current
is the horizontal near-surface orbital velocity of the long wave.

The second important relation is the conservation of wave crests
\cite{phillips1981dispersion}:

@@

As the short waves ride on the surface of the long wave,
they move in an accelerated reference frame and will thus experience effective
gravitational acceleration that changes in both space and time \cite{longuet1986eulerian,longuet1987propagation}.
Inserting Eq. (\ref{eq:dispersion}) into (\ref{eq:wave_action}) we obtain:

@@

\begin{equation}
\label{eq:wave_action2}
\dfrac{\partial N}{\partial t}
+ \left(C_g + U\right) \dfrac{\partial N}{\partial x}
+ N \dfrac{\partial U}{\partial x}
+ N \dfrac{\partial C_g}{\partial x}
= 0
\end{equation}
This equation is similar to Eq. \ref{eq:wavenumber}, except for the last term
which here represents the inhomogeneity of the group speed.
As \citeA{peureux2021unsteady} explained, this term is responsible for unstable
growth of wave action in infinite long-wave trains.
Eqs. \ref{eq:wavenumber} and \ref{eq:wave_action2} will be the governing equations
that we solve numerically in section \ref{section:numerical_solutions}.

@@

Eqs. \ref{eq:dispersion}-\ref{eq:w_L} is the full system of equations that we
exploit in the remainder of this paper.
Note that here we derive the solutions from a different starting set of
equations than that of \citeA{longuet1960changes}.
Rather than starting from the conservation of crests and wave action, as we do
here, they derived their solution from the linear superposition of the velocity
potential of two waves.
It appears the starting from the conservation of crests and wave action allows
for a simpler and more intuitive derivation.

@@

\begin{equation}
\label{eq:wavenumber2}
\dfrac{\partial k}{\partial t}
= - k \dfrac{\partial U}{\partial x}
\end{equation}
Although \citeA{peureux2021unsteady} pointed out that the solution by L-HS
requires assuming homogeneous group speed of the short-wave field, in fact,
it also requires assuming no horizontal propagation and advection of the short
waves.
Combining Eqs. \ref{eq:U_L} and \ref{eq:wavenumber2}, and integrating it in time
yields:

@@

\begin{figure}[ht]
\label{fig:analytical_solutions_ak0.1}
\centering
\includegraphics[width=0.8\textwidth]{figures/fig_analytical_solutions_ak0.1.png}
\caption{
  Modulation of short-wave (a) wavenumber, (b) gravitational acceleration,
  (c) amplitude, (d) steepness, (e) intrinsic frequency, and (d) intrinsic phase
  speed as function of long-wave phase for $\varepsilon_L = 0.1$, based on
  analytical solutions by \citeA{longuet1960changes} (L-HS 1960, black)
  and this paper (blue).
  Long-wave crest and trough are located at $\psi = 0$ and $\psi = \pi$,
  respectively.
}
\end{figure}

@@

Long waves induce orbital accelerations, so the short waves that ride on their
surface move in an accelerated reference frame and experience effective
gravitational acceleration that is lower at the crests and higher in the troughs
\cite{longuet1986eulerian,longuet1987propagation}.
Further, a smaller but non-negligible effect is that of the centripetal force
due to the curvature of the long wave
\cite{phillips1981dispersion,zhang1990evolution}.
These effects are completely described by projecting the gravitational
acceleration from the coordinate that is perpendicular to the mean water surface
($z=0$) to that which is perpendicular to the long-wave surface ($z=\eta$),
and likewise for the long-wave orbital accelerations:

@@

\begin{figure}[h]
\label{fig:effective_gravities}
\centering
\includegraphics[width=0.6\textwidth]{figures/fig_effective_gravities.png}
\caption{
  (a) Analytical solutions for the effective gravitational acceleration
  modulation by long waves, as function of long-wave phase, for $\varepsilon_L = 0.2$.
  Black is for linear wave evaluated at $z=0$,
  blue and green are for linear and Stokes waves, respectively, evaluated at $z=\eta$ and without curvature effects,
  and orange and green are for linear and Stokes waves, respectively, evaluated at $z=\eta$ and with curvature effects.
  (b) As in (a) but normalized by the modulation of the linear wave evaluated at $z=0$.
}
\end{figure}

\begin{figure}[h]
\label{fig:effective_gravities_mean_max_min}
\centering
\includegraphics[width=0.8\textwidth]{figures/fig_effective_gravities_mean_max_min.png}
\caption{
  As Fig. \ref{fig:effective_gravities} but showing the mean (solid),
  maximum (dashed), and minimum (dotted) short-wave gravity modulation as
  function of long-wave steepness $\varepsilon_L$.
}
\end{figure}

@@

\begin{figure}[ht]
\label{fig:analytical_solutions_ak0.2}
\centering
\includegraphics[width=0.8\textwidth]{figures/fig_analytical_solutions_ak0.2.png}
\caption{As Fig. \ref{fig:analytical_solutions_ak0.1} but for $\varepsilon_L = 0.2$.}
\end{figure}

\begin{figure}[ht]
\label{fig:analytical_solutions_ak0.4}
\centering
\includegraphics[width=0.8\textwidth]{figures/fig_analytical_solutions_ak0.4.png}
\caption{As Fig. \ref{fig:analytical_solutions_ak0.1} but for $\varepsilon_L = 0.4$.}
\end{figure}

@@

We now proceed to integrate the full numerical solutions for the short-wave
wavenumber and action density in presence of long waves, and in absence of
sources or sinks of wave energy.
Equations (\ref{eq:wavenumber})-(\ref{eq:wave_action2}) are discretized using
2$^{nd}$  order central finite difference in space and integrated in time using the
4$^{th}$ order Runge-Kutta method \cite{butcher1996runge}.
The space is divided into 100 grid points.
This is effectively the same equation set and numerical configuration as that of
\citeA{peureux2021unsteady}, except that, like \citeA{longuet1960changes}, their
long-wave orbital velocities are evaluated at $z=0$ instead of $z=\eta_L$.
The key difference is that evaluating orbital velocities at $z=0$ neglects the
Stokes drift of short-wave groups.
Although not significantly consequential for the modulation results here, there
is no good reason to exclude it given that its implementation is trivial.

Another difference is the choice of the numerical scheme for spatial differences,
which in their case is the MUSCL4 scheme by Kurganov and Tadmor (2000 TODO).
Although the 2$^{nd}$ order central finite difference is not appropriate for many
numerical problems, in our case it is sufficient because it is conservative and
the fields that we compute derivatives of are smooth and continuous.
We show in the next section that our numerical results in infinite long-wave
trains are qualitatively equivalent to those of \citeA{peureux2021unsteady}.

Finally, the numerical equations here are integrated in a fixed reference frame,
rather than one that moves with the long wave phase speed.
Either approach produces qualitatively equivalent results, but we find that
a fixed reference frame allows for more intuitive interpretation of the results.
However, this difference is important to keep in mind when comparing the results
of \citeA{peureux2021unsteady} and those presented here--in their Fig. 1 the
long-wave phase is fixed and the short waves are moving leftward
with the speed of $C_{pL} - C_g - U$ (neglecting any group speed inhomogeneity),
whereas in the figures that follow, the long wave is moving rightward with its
phase speed $C_{pL}$ and the short waves (that is, their energy) are moving
rightward with the speed of $C_g + U$ (neglecting any group wave inhomogeneity).

@@

\begin{figure}[h]
\label{fig:numerical_solutions}
\centering
\includegraphics[width=\textwidth]{figures/numerical_vs_analytical_solutions_with_phase.png}
\caption{
  Comparison of numerical solutions of wavenumber, amplitude, and steepness modulation
  with their analytical solutions, for $\varepsilon_L$ = 0.1, 0.2, and 0.4.
}
\end{figure}

\begin{figure}[h]
\label{fig:numerical_vs_analytical_k}
\centering
\includegraphics[width=0.6\textwidth]{figures/numerical_vs_analytical_solutions_k.png}
\caption{}
\end{figure}

\begin{figure}[h]
\label{fig:numerical_vs_analytical_a}
\centering
\includegraphics[width=0.6\textwidth]{figures/numerical_vs_analytical_solutions_a.png}
\caption{}
\end{figure}

\begin{figure}[h]
\label{fig:numerical_vs_analytical_ak}
\centering
\includegraphics[width=0.6\textwidth]{figures/numerical_vs_analytical_solutions_ak.png}
\caption{}
\end{figure}

@@

The key result of \citeA{peureux2021unsteady} is that of unsteady steepening of
short waves when a homogeneous field of short waves is forced by an infinite
long-wave train.
The steepening is driven by the progressive increase in the action of short
waves (as opposed to their wavenumber), and is centered on the group of short
waves that begins its journey in the trough of the long wave.
This is because the unmodulated short waves that begin in the trough enter into
the area where the surface velocities are converging.
Inversely, the short waves that begin around the crest of the long-wave will
enter into the area of surface divergence and will thus have their wave action
and wavenumber, decreased.
We reproduce this behavior in Fig. \ref{fig:modulation_3panel_infinite}, which
shows the evolution of the short-wave action, wavenumber, and steepness
modulation (here defined as the change of a quantity relative to its initial value).
After 10 long-wave periods, the short-wave action modulation $\widetilde{N}/N$
is approximately doubled, which almost exactly corresponds to the unsteady growth
reported by \citeA{peureux2021unsteady} in their Fig. 1.
Another important property of this solution is that the short-wave group that
experiences peak amplification (dampening) are not locked-in to the long-wave
crests (troughs), as they are in the L-HS solution.

\begin{figure}[h]
\label{fig:modulation_3panel_infinite}
\centering
\includegraphics[width=\textwidth]{figures/fig_modulation_3panel_infinite_wave_train.png}
\caption{
  Change in the short-wave action (left), wavenumber (middle), and steepness (right)
  relative to their initial values as function of initial long-wave phase and time.
  $k_L = 1$, $k = 10$, $\varepsilon_L = 0.1$.
}
\end{figure}

Why does this unsteady growth of short-wave action occur?
As \citeA{peureux2021unsteady} explain, "the additional change in advection
velocity due to the modulation of the short wave group speed gives an additional
amplification."
That is, it is the inhomogeneity term $N \dfrac{\partial C_g}{\partial x}$ that
is responsible for the instability.
However, the instability only occurs if the short waves are initialized as a
uniform field.
If they are initialized instead as a periodic function of the long-wave phase
such that their wavenumber (and optionally, action) is higher on the crests
and lower in the troughs, akin to the L-HS solution, the instability does not
occur.

\begin{figure}[h]
\label{fig:modulation_3panel_ramp}
\centering
\includegraphics[width=\textwidth]{figures/fig_modulation_3panel_linear_ramp.png}
\caption{
  Same as Fig. \ref{fig:modulation_3panel_infinite} but with a linear ramp
  applied to $a_L$ during the initial five long-wave periods.
}
\end{figure}

Why is it, then, that the solution is so different depending on the short-wave
initial conditions?
\citeA{peureux2021unsteady} did not provide an explanation for this behavior.
At first, it may seem that there is something special about the uniform initial
conditions that makes its solutions grow unsteadily and indefinitely.
\citeA{peureux2021unsteady} describe this scenario as "...the sudden appearance
of a long wave perturbation in the middle of a homogeneous short wave field".
The sudden appearance of long waves may be a clue.
The exact numerical simulation as shown in Fig. \ref{fig:modulation_3panel_infinite},
except for a linear ramp applied to $a_L$ (and consequently, $U$ and $W$ as well)
for the first five periods reveals that the unsteady growh no longer occurs
(Fig. \ref{fig:modulation_3panel_ramp}).

\begin{figure}[h]
  \label{fig:unsteady_growth_timeseries}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/fig_modulation_ramp_timeseries.png}
  \caption{
    Maximum short-wave steepness modulation as function of time in case of
    infinite long-wave train case (blue) and the same case but with a linear
    ramp during the initial five long-wave periods (orange). The dashed black
    line corresponds to the short-wave steepness of 0.4 at which most waves are
    expected to break.
  }
  \end{figure}

@@

\acknowledgments
Thanks to Nathan Laxague, Fabrice Ardhuin, Nick Pizzo, and Peisen Tan for the
helpful discussions.

\bibliography{references.bib}

>>>>

\documentclass[lineno]{jfm}

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\hypersetup{
    colorlinks = true,
    urlcolor   = blue,
    citecolor  = black,
}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newcommand{\RomanNumeralCaps}[1]
\linenumbers

% {\MakeUppercase{\romannumeral #1}}

\title{Revisiting the hydrodynamic wave modulation from linear wave theory}

\author{
  Milan Curcic\aff{1}
  \corresp{\email{mcurcic@miami.edu}}
}

\affiliation{
  \aff{1}Rosenstiel School of Marine, Atmospheric, and Earth Science, University of Miami, Miami, FL
  \aff{2}Frost Institute for Data Science and Computing, University of Miami, Coral Gables, FL
}

\begin{document}
\maketitle

\begin{abstract}
Hydrodynamic modulation of short ocean surface waves by longer ambient waves is
a well-known ocean surface process that affects remote sensing, the
interpretation of \textit{in situ} wave measurements, and numerical wave
forecasting.
In this paper, we revisit the linear wave theory and derive higher-order
solutions for the change of short-wave wavenumber, action density, and
gravitational acceleration due to the presence of longer waves.
We validate the analytical solutions with numerical simulations of the full wave
crest and action conservation equations.
The nonlinear analytical solutions of short-wave wavenumber, amplitude, and
steepness modulation significantly deviate from the linear analytical solutions
of \citet{longuet1960changes}, and are similar to the nonlinear numerical
solutions by \citet{zhang1990evolution}.
We also discuss the result of \citet{peureux2021unsteady} who found through
numerical simulations that the short-wave modulation grows unsteadily with
each long-wave phase.
Here we show that this unsteady growth only occurs for homogeneous initial
conditions and does not occur for more realistic long-wave groups.
Finally, the combined analytical and numerical framework allows us to quantify
the contribution of various terms in the full wave conservation equations.
The new analytical solutions are a good approximation of the full numerical
solution in long-wave steepness up to $\approx 0.2$.
\end{abstract}

\begin{keywords}
%Authors should not enter keywords on the manuscript, as these must be chosen by the author during the online submission process and will then be added during the typesetting process (see \href{https://www.cambridge.org/core/journals/journal-of-fluid-mechanics/information/list-of-keywords}{Keyword PDF} for the full list).  Other classifications will be added at the same time.
\end{keywords}

%{\bf MSC Codes }  {\it(Optional)} Please enter your MSC Codes here

@@

Short ocean surface waves are modulated by longer swell.
Following the result by \citet{unna1941white,unna1942waves,unna1947sea},
\citet{longuet1960changes} introduced an analytical solution for hydrodynamic
modulation of short waves at the crest of an underlying longer wave:

\begin{equation}
\label{eq:lhs1960wavenumber}
\widetilde{k} = k (1 + \varepsilon_L)
\end{equation}
where $\widetilde{k}$ and $k$ are modulated and unmodulated short-wave wavenumbers,
respectively, and $\varepsilon_L = a_L k_L$ is the steepness of the long wave with
wavenumber $k_L$ and amplitude $a_L$.
This result has been influential on the development of remote sensing of ocean
surface waves and currents \citep{keller1975microwave,hara1994hydrodynamic}.
\citet{longuet1987propagation} revisited this problem by considering variation
in the gravitational acceleration and fully non-linear wave numerical solutions
to find significantly stronger modulation than that predicted by
Eq. \ref{eq:lhs1960wavenumber}.
\citet{zhang1990evolution} evaluated the effects of nonlinearity of short waves
using a non-linear Schr\" odinger equation and found higher wavenumber
modulation but lesser amplitude modulation than those predicted by
\citet{longuet1987propagation}.
More recently, \citep{peureux2021unsteady} simulated the full wave conservation
equations and found that the short waves grow unsteadily due to the propagation of
longer waves, suggesting that the steady-state solutions may only be valid for
a few long-wave periods before the short waves are steep enough to break.

\begin{table}
\begin{center}
\def~{\hphantom{0}}
\begin{tabular}{cccccc}
Reference   & Governing & Gravity & Nonlinear  & Nonlinear   & Solution \\
            & equations & varies  & long waves & short waves &          \\
\hline
L-HS 1960   & Velocity potential       & No  & No  & No  & Analytical \\
\hline
P 1981      & Crest and energy         & Yes & Yes & No  & Numerical \\
            & conservation             &     &     &     &           \\
\hline
L-H 1987    & Velocity potential       & Yes & Yes & No  & Numerical \\
\hline
H 1988      & Hamiltonian              & Yes & Yes & No  & Analytical \\
\hline
ZM 1990     & Nonlinear Schr\" odinger & Yes & Yes & Yes & Numerical \\
            & equation                 &     &     &     &           \\
\hline
PAG 2021    & Crest and action         & Yes & No & No  & Numerical \\
            & conservation             &     &     &     &           \\
\hline
This paper  & Crest and action         & Yes & Yes* & No  & Analytical \\
            & conservation             &     &      &     & and numerical \\
\hline
\end{tabular}
\caption{
  Summary of prior
  \citep{longuet1960changes,phillips1981dispersion,longuet1987propagation,zhang1990evolution,peureux2021unsteady}
  and present (this paper) approaches to calculating the modulation of short
  waves by long waves.
  *: long 3rd order Stokes wave is considered only in numerical simulations.
}
\label{table:modulation_literature_summary}
\end{center}
\end{table}

@@

\begin{equation}
\label{eq:dispersion}
\omega = \sqrt{gk} + k U
\end{equation}
where $\omega$ is the angular frequency, $g$ is the gravitational acceleration,
$k$ is the wavenumber, and $U$ is the mean advective current in the direction
of the wave propagation.
A current in the direction of the waves thus increases its absolution frequency,
wavenumber remaining unchanged.
An important limitation here is that $U$ must be slow-varying on the scales of
the wave period \citep{bretherton1968wavetrains}.
In the context of short waves riding on long waves, the mean advective current
is the horizontal near-surface orbital velocity of the long wave.

The second important relation is the conservation of wave crests
\citep{phillips1981dispersion}:

@@

As the short waves ride on the surface of the long wave,
they move in an accelerated reference frame and will thus experience effective
gravitational acceleration that changes in both space and time
\citep{longuet1986eulerian,longuet1987propagation}.
Inserting Eq. (\ref{eq:dispersion}) into (\ref{eq:wave_action}) we obtain:

@@

\begin{equation}
\label{eq:wave_action2}
\dfrac{\partial N}{\partial t}
+ \left(C_g + U\right) \dfrac{\partial N}{\partial x}
+ N \dfrac{\partial U}{\partial x}
+ N \dfrac{\partial C_g}{\partial x}
= 0
\end{equation}
This equation is similar to Eq. \ref{eq:wavenumber}, except for the last term
which here represents the inhomogeneity of the group speed.
As \citet{peureux2021unsteady} explained, this term is responsible for unstable
growth of wave action in infinite long-wave trains.
Eqs. \ref{eq:wavenumber} and \ref{eq:wave_action2} will be the governing equations
that we solve numerically in section \ref{section:numerical_solutions}.

@@

Eqs. \ref{eq:dispersion}-\ref{eq:w_L} is the full system of equations that we
exploit in the remainder of this paper.
Note that here we derive the solutions from a different starting set of
equations than that of \citet{longuet1960changes}.
Rather than starting from the conservation of crests and wave action, as we do
here, they derived their solution from the linear superposition of the velocity
potential of two waves.
It appears the starting from the conservation of crests and wave action allows
for a simpler and more intuitive derivation.

@@

\begin{equation}
\label{eq:wavenumber2}
\dfrac{\partial k}{\partial t}
= - k \dfrac{\partial U}{\partial x}
\end{equation}
Although \citet{peureux2021unsteady} pointed out that the solution by L-HS
requires assuming homogeneous group speed of the short-wave field, in fact,
it also requires assuming no horizontal propagation and advection of the short
waves.
Combining Eqs. \ref{eq:U_L} and \ref{eq:wavenumber2}, and integrating it in time
yields:

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/fig_analytical_solutions_ak0.1.png}
\caption{
  Modulation of short-wave (a) wavenumber, (b) gravitational acceleration,
  (c) amplitude, (d) steepness, (e) intrinsic frequency, and (d) intrinsic phase
  speed as function of long-wave phase for $\varepsilon_L = 0.1$, based on
  analytical solutions by \citet{longuet1960changes} (L-HS 1960, black)
  and this paper (blue).
  Long-wave crest and trough are located at $\psi = 0$ and $\psi = \pi$,
  respectively.
}
\label{fig:analytical_solutions_ak0.1}
\end{figure}

@@

Long waves induce orbital accelerations, so the short waves that ride on their
surface move in an accelerated reference frame and experience effective
gravitational acceleration that is lower at the crests and higher in the troughs
\citep{longuet1986eulerian,longuet1987propagation}.
Further, a smaller but non-negligible effect is that of the centripetal force
due to the curvature of the long wave
\citep{phillips1981dispersion,zhang1990evolution}.
These effects are completely described by projecting the gravitational
acceleration from the coordinate that is perpendicular to the mean water surface
($z=0$) to that which is perpendicular to the long-wave surface ($z=\eta$),
and likewise for the long-wave orbital accelerations:

@@

\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{figures/fig_effective_gravities.png}
\caption{
  (a) Analytical solutions for the effective gravitational acceleration
  modulation by long waves, as function of long-wave phase, for $\varepsilon_L = 0.2$.
  Black is for linear wave evaluated at $z=0$,
  blue and green are for linear and Stokes waves, respectively, evaluated at $z=\eta$ and without curvature effects,
  and orange and green are for linear and Stokes waves, respectively, evaluated at $z=\eta$ and with curvature effects.
  (b) As in (a) but normalized by the modulation of the linear wave evaluated at $z=0$.
}
\label{fig:effective_gravities}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/fig_effective_gravities_mean_max_min.png}
\caption{
  As Fig. \ref{fig:effective_gravities} but showing the mean (solid),
  maximum (dashed), and minimum (dotted) short-wave gravity modulation as
  function of long-wave steepness $\varepsilon_L$.
}
\label{fig:effective_gravities_mean_max_min}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/fig_analytical_solutions_ak0.2.png}
\caption{As Fig. \ref{fig:analytical_solutions_ak0.1} but for $\varepsilon_L = 0.2$.}
\label{fig:analytical_solutions_ak0.2}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/fig_analytical_solutions_ak0.4.png}
\caption{As Fig. \ref{fig:analytical_solutions_ak0.1} but for $\varepsilon_L = 0.4$.}
\label{fig:analytical_solutions_ak0.4}
\end{figure}

@@

We now proceed to integrate the full numerical solutions for the short-wave
wavenumber and action density in presence of long waves, and in absence of
sources or sinks of wave energy.
Equations (\ref{eq:wavenumber})-(\ref{eq:wave_action2}) are discretized using
2$^{nd}$  order central finite difference in space and integrated in time using the
4$^{th}$ order Runge-Kutta method \citep{butcher1996runge}.
The space is divided into 100 grid points.
This is effectively the same equation set and numerical configuration as that of
\citet{peureux2021unsteady}, except that, like \citet{longuet1960changes}, their
long-wave orbital velocities are evaluated at $z=0$ instead of $z=\eta_L$.
The key difference is that evaluating orbital velocities at $z=0$ neglects the
Stokes drift of short-wave groups.
Although not significantly consequential for the modulation results here, there
is no good reason to exclude it given that its implementation is trivial.

Another difference is the choice of the numerical scheme for spatial differences,
which in their case is the MUSCL4 scheme by Kurganov and Tadmor (2000 TODO).
Although the 2$^{nd}$ order central finite difference is not appropriate for many
numerical problems, in our case it is sufficient because it is conservative and
the fields that we compute derivatives of are smooth and continuous.
We show in the next section that our numerical results in infinite long-wave
trains are qualitatively equivalent to those of \citet{peureux2021unsteady}.

Finally, the numerical equations here are integrated in a fixed reference frame,
rather than one that moves with the long wave phase speed.
Either approach produces qualitatively equivalent results, but we find that
a fixed reference frame allows for more intuitive interpretation of the results.
However, this difference is important to keep in mind when comparing the results
of \citet{peureux2021unsteady} and those presented here--in their Fig. 1 the
long-wave phase is fixed and the short waves are moving leftward
with the speed of $C_{pL} - C_g - U$ (neglecting any group speed inhomogeneity),
whereas in the figures that follow, the long wave is moving rightward with its
phase speed $C_{pL}$ and the short waves (that is, their energy) are moving
rightward with the speed of $C_g + U$ (neglecting any group wave inhomogeneity).

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/numerical_vs_analytical_solutions_with_phase.png}
\caption{
  Comparison of numerical solutions of wavenumber, amplitude, and steepness modulation
  with their analytical solutions, for $\varepsilon_L$ = 0.1, 0.2, and 0.4.
}
\label{fig:numerical_solutions}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{figures/numerical_vs_analytical_solutions_k.png}
\caption{}
\label{fig:numerical_vs_analytical_k}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{figures/numerical_vs_analytical_solutions_a.png}
\caption{}
\label{fig:numerical_vs_analytical_a}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{figures/numerical_vs_analytical_solutions_ak.png}
\caption{}
\label{fig:numerical_vs_analytical_ak}
\end{figure}

@@

The key result of \citet{peureux2021unsteady} is that of unsteady steepening of
short waves when a homogeneous field of short waves is forced by an infinite
long-wave train.
The steepening is driven by the progressive increase in the action of short
waves (as opposed to their wavenumber), and is centered on the group of short
waves that begins its journey in the trough of the long wave.
This is because the unmodulated short waves that begin in the trough enter into
the area where the surface velocities are converging.
Inversely, the short waves that begin around the crest of the long-wave will
enter into the area of surface divergence and will thus have their wave action
and wavenumber, decreased.
We reproduce this behavior in Fig. \ref{fig:modulation_3panel_infinite}, which
shows the evolution of the short-wave action, wavenumber, and steepness
modulation (here defined as the change of a quantity relative to its initial value).
After 10 long-wave periods, the short-wave action modulation $\widetilde{N}/N$
is approximately doubled, which almost exactly corresponds to the unsteady growth
reported by \citet{peureux2021unsteady} in their Fig. 1.
Another important property of this solution is that the short-wave group that
experiences peak amplification (dampening) are not locked-in to the long-wave
crests (troughs), as they are in the L-HS solution.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/fig_modulation_3panel_infinite_wave_train.png}
\caption{
  Change in the short-wave action (left), wavenumber (middle), and steepness (right)
  relative to their initial values as function of initial long-wave phase and time.
  $k_L = 1$, $k = 10$, $\varepsilon_L = 0.1$.
}
\label{fig:modulation_3panel_infinite}
\end{figure}

Why does this unsteady growth of short-wave action occur?
As \citet{peureux2021unsteady} explain, "the additional change in advection
velocity due to the modulation of the short wave group speed gives an additional
amplification."
That is, it is the inhomogeneity term $N \dfrac{\partial C_g}{\partial x}$ that
is responsible for the instability.
However, the instability only occurs if the short waves are initialized as a
uniform field.
If they are initialized instead as a periodic function of the long-wave phase
such that their wavenumber (and optionally, action) is higher on the crests
and lower in the troughs, akin to the L-HS solution, the instability does not
occur.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/fig_modulation_3panel_linear_ramp.png}
\caption{
  Same as Fig. \ref{fig:modulation_3panel_infinite} but with a linear ramp
  applied to $a_L$ during the initial five long-wave periods.
}
\label{fig:modulation_3panel_ramp}
\end{figure}

Why is it, then, that the solution is so different depending on the short-wave
initial conditions?
\citet{peureux2021unsteady} did not provide an explanation for this behavior.
At first, it may seem that there is something special about the uniform initial
conditions that makes its solutions grow unsteadily and indefinitely.
\citet{peureux2021unsteady} describe this scenario as "...the sudden appearance
of a long wave perturbation in the middle of a homogeneous short wave field".
The sudden appearance of long waves may be a clue.
The exact numerical simulation as shown in Fig. \ref{fig:modulation_3panel_infinite},
except for a linear ramp applied to $a_L$ (and consequently, $U$ and $W$ as well)
for the first five periods reveals that the unsteady growth no longer occurs
(Fig. \ref{fig:modulation_3panel_ramp}).

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/fig_modulation_ramp_timeseries.png}
  \caption{
    Maximum short-wave steepness modulation as function of time in case of
    infinite long-wave train case (blue) and the same case but with a linear
    ramp during the initial five long-wave periods (orange). The dashed black
    line corresponds to the short-wave steepness of 0.4 at which most waves are
    expected to break.
  }
  \label{fig:unsteady_growth_timeseries}
\end{figure}

@@

In this paper we revisited the problem of short-wave modulation by long waves
from a linear wave theory perspective.
Using the linearized wave crest and action conservation equations, coupled with
the nonlinear gravity modulation for short waves that includes the the curvature
effects of the long wave, we derived new analytical solutions for the modulation
of short wave wavenumber, amplitude, steepness, intrinsic frequency, and phase
speed.
The latter two have not been previously examined in the context of short-wave
modulation, but are important for correctly calculating the wind input into
short waves, which is proportional to the wind speed relative to the wave
celerity.
